---
title: Multilevel logistic regression on state presence, terrain features, and legal identity
  possession in Uttarakhand
output:
  word_document: default
  pdf_document: default
---

## Setup

```{r, setup, include = FALSE}
# Set working directory for all code chunks
knitr::opts_knit$set(root.dir = "/Users/anvitapant/Library/CloudStorage/OneDrive-UvA/Thesis/Quant/DHS 2015") 
# Replace the string with the path to your working directory

# Clean the environment
rm(list = ls())
```


```{r}
# Install and load required packages 
#install.packages("tidyverse")
#install.packages("readstata13")
#install.packages("lme4")
#install.packages("sjPlot")
#install.packages("modelsummary")
#install.packages("prediction") 
#install.packages("margins")
#install.packages("stargazer")
library(prediction)
library(stargazer)
library(margins)
library(modelsummary)
library(tidyverse)
library(readstata13) 
library(lme4) 
library(sjPlot) 
```

## Preparing a dataframe with relevant variables

```{r}
vars <- c("shdistri", "hv021", "hv270", "sh34", "sh36", "hv009", "hv024") 
# Variable names to include 

# Appending the variables for household member characteristics to the list of 
# variable names
headers_to_get <- vector()
header_prefixes = c("hv104_", "hv105_", "hv106_","hvidx_", "hv140_", "sh21a_")

for (prefix in header_prefixes) {
  for (i in 1:41) {
    headers_to_get <- append(headers_to_get, sprintf("%s%02d", prefix, i))
  }
}
# Appending the variable for mother's highest educational level to the list of 
# variable names
for (i in 1:9) {
    vars <- append(vars, sprintf("hc61_%d", i))
  }

vars <- append(vars, headers_to_get)
vars <- append("hhid", vars)

vars
```


```{r}
# Input of columns with the specific variable names 
dhs_15_df <- read.dta13("IAHR74FL.DTA", generate.factors=TRUE, 
                        missing.type = TRUE, select.cols = vars)

# Write to a .csv file for ease of retrieval
write.csv(dhs_15_df, file = "varsofinterest.csv") 

# Filtering the dataframe to only retain observations from Uttarakhand 
UK_df_wide <- dhs_15_df %>% 
  filter(hv024 == "uttarakhand")
```



```{r}
# Converting data from wide to long format: Information for each HH member is 
# currently presented in columns. I convert this to present information for 
# each household member in rows.
not_all_na <- function(x) any(!is.na(x))
HH_chars_df <- UK_df_wide %>% 
  select(where(not_all_na)) %>% 
  pivot_longer(cols = starts_with(c("hvidx_", "hv104_", "hv105_", "hv106_", 
                                    "hv140_", "sh21a_")),
               names_to = c(".value", "hvidx_values", "hv104_values",
                            "hv105_values", "hv106_values", "hv140_values",
                            "sh21a_values"),
               names_sep = "_") 
  
```

```{r}
# Mapping entries in columns hc61_[1-5] to values below age 5 in column 
# hv105
fill_hc61_data <- function(df) {
  children_rows <- df[as.integer(as.character(df[, "hv105"][[1]])) < 5,] %>% 
    filter( !if_all( c(hvidx), is.na ) ) %>% 
    select(hvidx) %>% 
    array
  
  children_rows <- children_rows[[1]]
  newcol = rep(NA, nrow(df))
  
  if (is.na(children_rows[1])) {
    return(newcol)
  }
  
  # This contains all data for any household
  household_id <- df[1, "hhid"][[1]]
  household_row <- UK_df_wide[UK_df_wide$hhid == household_id,]
  
  for (idx in 1:length(children_rows) ) {
    rownumber = children_rows[idx]
    value <- household_row[sprintf("hc61_%d", idx)][[1]]
    newcol[rownumber] <- as.character(value)
  }
  return(newcol)
}
```

```{r}
# Applying the function to the entire dataframe to unnest data
options(warn = -1)
HH_bymember_df <- HH_chars_df %>% 
  group_by(hhid) %>% 
  do(data.frame(., hc61 = fill_hc61_data(.))) %>% 
  unnest
```

```{r}
# Retaining the relevant column names
HH_bymember_df <- HH_bymember_df[, !names(HH_bymember_df) %in% 
                                   append(c("hvidx_values",
                                            "hv104_values","hv105_values",
                                            "hv106_values", "hv140_values",
                                            "sh21a_values", "hc61_1", "hc61_2",
                                            "hc61_3", "hc61_4", "hc61_5"),
                                          headers_to_get)] 

# Renaming columns in the new dataframe
oldcolnames <- c(names(HH_bymember_df))
newcolnames <- c("case_id", "num_HH_members", "psu", "state", "wealth_idx", 
                 "district", "HH_head_religion", "HH_head_caste", 
                 "HH_member_idx", "sex", "age", "edu_lvl", "birth_cert", 
                 "has_aadhaar", "mother_edu_lvl")
HH_bymember_df_renamedcols <- HH_bymember_df %>% 
  select(all_of(oldcolnames)) %>%
  rename_with(~ newcolnames[which(oldcolnames == .x)])
HH_bymember_df_renamedcols
```

```{r}
# Write to a .csv file for ease of retrieval
write_csv(HH_bymember_df_renamedcols, "tidied_data.csv") 
```

```{r}
# Get summary statistics of our tidied data
summary(HH_bymember_df_renamedcols)
```

## Handling missing data

```{r}
# Count missing values in each column of the overall dataframe
sapply(HH_bymember_df_renamedcols, function(x) sum(is.na(x)))

# Overall missing value count in our dataframe
sum(is.na(HH_bymember_df_renamedcols))
```

```{r}
# Checking for unique values in the age column of the overall dataframe
unique(HH_bymember_df_renamedcols$age)
```

```{r}
# Replacing the values for "95+" and "don't know" in the age column
replaced_age_vals <- HH_bymember_df_renamedcols$age %>% 
  gsub("95\\+", 100, .) %>% 
  gsub("don't know", NA, .)

HH_bymember_df_renamedcols$age <- replaced_age_vals
```

```{r}
# Filter the overall dataframe for characteristics of children under 
# 5 years of age
HH_children_df <- HH_bymember_df_renamedcols %>% 
  filter(as.integer(as.character(age)) < 5)
HH_children_df
```

```{r}
# Count missing values in each column of the dataframe with values for 
# children under 5
sapply(HH_children_df, function(x) sum(is.na(x)))

# Overall missing value count in the dataframe with values for children under 5
sum(is.na(HH_children_df))
```

```{r}
# Filter the overall dataframe for characteristics of anyone at or above
# 5 years of age
HH_othermems_df <- HH_bymember_df_renamedcols %>% 
  filter(as.integer(as.character(age)) >= 5 | is.na(age) | age == 100)
```


```{r}
# Retaining the relevant column names of the dataframe with values for anyone 
# at or above 5 years of age
droppedcols <- c("birth_cert", "mother_edu_lvl")
HH_othermems_df <- HH_othermems_df[, !names(HH_othermems_df) %in% droppedcols] 
HH_othermems_df
```

```{r}
# Count missing values in each column of the dataframe with values for anyone at
# or above 5 years of age
sapply(HH_othermems_df, function(x) sum(is.na(x)))

# Overall missing value count in the dataframe with values for anyone at or above 
# 5 years of age
sum(is.na(HH_othermems_df))
```

```{r}
# Number of rows in dataframe with values for children under 5 before dropping
# missing observations
nrow(HH_children_df)

# Number of rows in dataframe with values for anyone at or above 5 years of age 
# before dropping missing observations
nrow(HH_othermems_df)
```

```{r}
# Exclude rows having missing data from dataframe with values for children 
# under 5 for ANY variable
HH_children_df_no_NA1 <- HH_children_df %>% 
  drop_na()
HH_children_df_no_NA <- HH_children_df_no_NA1 %>%
  filter(mother_edu_lvl != "don't know")

# Number of rows in dataframe with values for for children under 5 after 
# dropping missing observations
nrow(HH_children_df_no_NA)

# Write to a .csv file
write.csv(HH_children_df_no_NA, "HH_children_data_tidied_final.csv")
```

```{r}
# Exclude rows having missing data from dataframe with values for anyone at or 
# above 5 years of age for ANY variable
HH_othermems_df_no_NA <- HH_othermems_df %>% 
  drop_na()


# Number of rows in dataframe with values for anyone at or above 5 years of age 
# after dropping missing observations
nrow(HH_othermems_df_no_NA)

# Write to a .csv file
write.csv(HH_othermems_df_no_NA, "HH_othermembers_data_tidied_final.csv")
```


```{r}
# Now I load the variables for the spatial characteristics, keep values for 
# Uttarakhand districts for 2015, and save them as .csv files for easy retrieval
setwd("/Users/anvitapant/Library/CloudStorage/OneDrive-UvA/Thesis/Quant/SHRUG/shrug-forest cover-csv")
forest_cover <- read.csv("vcf_pc11dist.csv")
vars<-c("pc11_district_id","pc11_state_id","vcf_mean","year")
forest_cover_df <- forest_cover[,vars]
forest_cover_df$pc11_district_id <- as.numeric(forest_cover_df$pc11_district_id)
forest_cover_df <- forest_cover_df[forest_cover_df$pc11_district_id>055,]
forest_cover_df <- forest_cover_df[forest_cover_df$pc11_district_id<069,] 
forest_cover_df <- forest_cover_df[forest_cover_df$year>2014,]
forest_cover_df <- forest_cover_df[forest_cover_df$year<2016,]
write.csv(forest_cover_df, "forest_cover_UK_districts.csv")


setwd("/Users/anvitapant/Library/CloudStorage/OneDrive-UvA/Thesis/Quant/SHRUG/shrug-rugged-csv")
ruggedness <- read.csv("tri_pc11dist.csv")
vars<-c("pc11_district_id","pc11_state_id","tri_mean")
ruggedness_df <- ruggedness[,vars]
ruggedness_df$pc11_district_id <- as.numeric(ruggedness_df$pc11_district_id)
ruggedness_df <- ruggedness_df[ruggedness_df$pc11_district_id>055,]
ruggedness_df <- ruggedness_df[ruggedness_df$pc11_district_id<069,] 
write.csv(ruggedness_df, "ruggedness_UK districts.csv")


setwd("/Users/anvitapant/Library/CloudStorage/OneDrive-UvA/Thesis/Quant/SHRUG/shrug-night lights-annual-csv")
night_lights <- read.csv("viirs_annual_pc11dist.csv")
vars <- c("pc11_district_id",	"pc11_state_id", "viirs_annual_mean", "category", "year")
night_lights_df <- night_lights[,vars]
night_lights_df$pc11_district_id <- as.numeric(night_lights_df$pc11_district_id)
night_lights_df$category <- as.character(night_lights_df$category)
night_lights_df <- night_lights_df[night_lights_df$category != "median-masked",]
night_lights_df <- night_lights_df[night_lights_df$pc11_district_id>055,]
night_lights_df <- night_lights_df[night_lights_df$pc11_district_id<069,] 
night_lights_df <- night_lights_df[night_lights_df$year>2014,]
night_lights_df <- night_lights_df[night_lights_df$year<2016,]
write.csv(night_lights_df, "night_lights_UK_districts.csv")
```

```{r}
# Merge the 3 data tables with the spatial characteristics into one dataframe
spatial_dfs_list <- list(forest_cover_df, night_lights_df, ruggedness_df)
spatial_df <- spatial_dfs_list %>% 
  reduce(left_join, by = "pc11_district_id")
```

```{r}
# Recode the values of the district variable for the spatial variables dataframe
spatial_df <- spatial_df %>% 
rename(district = pc11_district_id)
spatial_df[[1]] <- case_match(
      spatial_df[[1]],
      56 ~ "uttarkashi",
      57 ~ "chamoli",
      58 ~ "rudraprayag",
      59 ~ "tehri garhwal",
      60 ~ "dehradun",
      61 ~ "garhwal",
      62 ~ "pithoragarh",
      63 ~ "bageshwar",
      64 ~ "almora",
      65 ~ "champawat",
      66 ~ "nainital",
      67 ~ "udham singh nagar",
      68 ~ "hardwar"
    )
spatial_df
```

Do a left-join of the dataframes to combine spatial, district level variables 
with individual characteristics in each row

```{r}
HH_children_left_merged_df <- merge(HH_children_df_no_NA,
                                    spatial_df,
                                    by = "district",
                                    all.x = TRUE)

head(HH_children_left_merged_df[c("case_id", "viirs_annual_mean", "vcf_mean", 
                                  "tri_mean")])
```

```{r}
# Do a left-join of the dataframes with variables for household members of ages 
# 5 and above and spatial characteristics
HH_othermems_left_merged_df <- merge(HH_othermems_df_no_NA,
                                    spatial_df,
                                    by = "district",
                                    all.x = TRUE)
```

## Dummy coding a few categorical variables in preparation for regression

```{r}
# Drop unused factor levels from the dataframe
HH_children_left_merged_df <- droplevels(HH_children_left_merged_df)
HH_othermems_left_merged_df <- droplevels(HH_othermems_left_merged_df)

```

### For children under 5 years of age

```{r}
# Creating dummy variables for the household head's religion
HH_children_left_merged_df <- HH_children_left_merged_df %>%
  mutate(HH_head_religion_hindu = ifelse(HH_head_religion == "hindu", 1, 0),
         HH_head_religion_muslim = ifelse(HH_head_religion == "muslim", 1, 0),
         HH_head_religion_sikh = ifelse(HH_head_religion == "sikh", 1, 0),
         HH_head_religion_others = case_when(
           HH_head_religion %in% c("christian", "buddhist/neo-buddhist", "parsi/zoroastrian", "other") ~ 1,
           TRUE ~ 0))

```

```{r}
# Creating a dummy variable for birth certificate possession 
HH_children_left_merged_df$birth_cert_recoded <-
  HH_children_left_merged_df$birth_cert
HH_children_left_merged_df$birth_cert_recoded <- case_match(
  HH_children_left_merged_df$birth_cert_recoded,
  "has certificate" ~ 1,
  c("neither certificate or registered", "registered", "don't know") ~ 0
)
```

```{r}
# Selecting reference factor categorical variables for regressions
HH_children_left_merged_df$district <- relevel(HH_children_left_merged_df$district, "dehradun")
HH_children_left_merged_df$HH_head_caste <- relevel(HH_children_left_merged_df$HH_head_caste, "none of above")
HH_children_left_merged_df$sex <- relevel(HH_children_left_merged_df$sex, "male")
HH_children_left_merged_df$wealth_idx <- relevel(HH_children_left_merged_df$wealth_idx, "poorest")
# Changing the mother's education level variable into a factor
HH_children_left_merged_df$mother_edu_lvl <- as.factor(HH_children_left_merged_df$mother_edu_lvl)
HH_children_left_merged_df$mother_edu_lvl <- relevel(HH_children_left_merged_df$mother_edu_lvl, "no education")

```

###  For household members of ages 5 and above

```{r}
# Creating dummy variables for the household head's religion
HH_othermems_left_merged_df <- HH_othermems_left_merged_df %>%
  mutate(HH_head_religion_hindu_othermems = ifelse(HH_head_religion == "hindu", 1, 0),
         HH_head_religion_muslim_othermems = ifelse(HH_head_religion == "muslim", 1, 0),
         HH_head_religion_sikh_othermems = ifelse(HH_head_religion == "sikh", 1, 0),
         HH_head_religion_others_othermems = case_when(
           HH_head_religion %in% c("christian", "buddhist/neo-buddhist", "parsi/zoroastrian", "other") ~ 1,
           TRUE ~ 0))
```

```{r}
# Creating a dummy variable for Aadhaar card possession
HH_othermems_left_merged_df$has_aadhaar_recoded <-
  HH_othermems_left_merged_df$has_aadhaar
HH_othermems_left_merged_df$has_aadhaar_recoded <- case_match(HH_othermems_left_merged_df$has_aadhaar_recoded,
                                                     "yes" ~ 1,
                                                     c("no", "don't know") ~ 0)
```

```{r}
# Selecting reference factor categorical variables for regressions
HH_othermems_left_merged_df$district <- relevel(HH_othermems_left_merged_df$district, "dehradun")
HH_othermems_left_merged_df$HH_head_caste <- relevel(HH_othermems_left_merged_df$HH_head_caste, "none of above")
HH_othermems_left_merged_df$sex <- relevel(HH_othermems_left_merged_df$sex, "male")
HH_othermems_left_merged_df$wealth_idx <- relevel(HH_othermems_left_merged_df$wealth_idx, "poorest")
# Changing the education level variable into a factor
HH_othermems_left_merged_df$edu_lvl <- as.factor(HH_othermems_left_merged_df$edu_lvl)
HH_othermems_left_merged_df$edu_lvl <- relevel(HH_othermems_left_merged_df$edu_lvl,
                                               "no education, preschool")

```

## Rate of possession of BC and Aadhaar
```{r}
# Calculating district possession rates for birth certificate
possession_rates1 <- HH_children_left_merged_df %>%
  group_by(district) %>%
 summarize(
    total_population = n(),
    possession_count = sum(birth_cert_recoded),
    possession_rate = mean(birth_cert_recoded) * 100
  )

possession_rates_df1 <- as.data.frame(possession_rates1)
possession_rates_df1$non_possession <- possession_rates_df1$total_population - possession_rates_df1$possession_count

contingency_table1 <- data.frame(
  possession1 = possession_rates_df1$possession_count,
  non_possession = possession_rates_df1$non_possession,
  row.names = possession_rates_df1$district
)

print(contingency_table1)

chi_squared_result1 <- chisq.test(contingency_table1)

# View the results
print(chi_squared_result1)

write.csv(possession_rates1, "possession_rates1.csv", row.names = FALSE)


# Calculating district possession rates for Aadhaar 
possession_rates <- HH_othermems_left_merged_df %>%
  group_by(district) %>%
 summarize(
    total_population = n(),
    possession_count = sum(has_aadhaar_recoded),
    possession_rate = mean(has_aadhaar_recoded) * 100
  )

possession_rates_df <- as.data.frame(possession_rates)
possession_rates_df$non_possession <- possession_rates_df$total_population - possession_rates_df$possession_count

contingency_table <- data.frame(
  possession = possession_rates_df$possession_count,
  non_possession = possession_rates_df$non_possession,
  row.names = possession_rates_df$district
)

print(contingency_table)

chi_squared_result <- chisq.test(contingency_table)

# View the results
print(chi_squared_result)

write.csv(possession_rates, "possession_rates.csv", row.names = FALSE)
```

## Regression analyses

### Preliminary phase

```{r}
# Grand-mean centering the level 2 variables

# Forest cover
HH_children_left_merged_df$vcf_mean <- HH_children_left_merged_df$vcf_mean - mean(HH_children_left_merged_df$vcf_mean)
HH_othermems_left_merged_df$vcf_mean <- HH_othermems_left_merged_df$vcf_mean - mean(HH_othermems_left_merged_df$vcf_mean)

# Ruggedness
HH_children_left_merged_df$tri_mean <- HH_children_left_merged_df$tri_mean - mean(HH_children_left_merged_df$tri_mean)
HH_othermems_left_merged_df$tri_mean <- HH_othermems_left_merged_df$tri_mean - mean(HH_othermems_left_merged_df$tri_mean)

# Night lights
HH_children_left_merged_df$viirs_annual_mean <- HH_children_left_merged_df$viirs_annual_mean - mean(HH_children_left_merged_df$viirs_annual_mean)
HH_othermems_left_merged_df$viirs_annual_mean <- HH_othermems_left_merged_df$viirs_annual_mean - mean(HH_othermems_left_merged_df$viirs_annual_mean)


```

### Simple logit model with all variables on the same level

#### Birth certificate possession

```{r}
# Running a simple regression with all level 1 and level 2 variables at the 
# same level

M1_birth_cert <- glm(
  birth_cert_recoded ~ sex + wealth_idx + mother_edu_lvl
  + HH_head_religion_muslim + HH_head_religion_sikh + HH_head_religion_others 
  + HH_head_caste +  viirs_annual_mean + tri_mean + vcf_mean,
  data = HH_children_left_merged_df,
  family = binomial(link = "logit")
)
summary(M1_birth_cert)
tab_model(M1_birth_cert)
M1_birth_cert_margins <- margins(M1_birth_cert)
M1_birth_cert_summary <- summary(M1_birth_cert_margins)
write.csv(M1_birth_cert_summary, "M1_birth_cert_summary.csv")
tab_model(M1_birth_cert)

```

```{r}
# Running a simple regression with all level 1 and level 2 variables at 
# the same level
M1_aadhaar <- glm(
  has_aadhaar_recoded ~ sex + wealth_idx + edu_lvl
   + HH_head_religion_muslim_othermems + HH_head_religion_sikh_othermems
  + HH_head_religion_others_othermems  
  + HH_head_caste + viirs_annual_mean + tri_mean + vcf_mean,
  data = HH_othermems_left_merged_df,
  family = binomial(link = "logit")
)
summary(M1_aadhaar)
tab_model(M1_aadhaar)
M1_aadhaar_margins <- margins(M1_aadhaar)
M1_aadhaar_margins_summary <- summary(M1_aadhaar_margins)
write.csv(M1_aadhaar_margins_summary, "M1_aadhaar_margins_summary.csv")

```
 
### Multilevel models

First, I created empty models to ascertain how much variance can be explained 
by individual and district level factors.

#### Birth certificate possession

```{r}
#The null model, with a random intercept was created and tested, in 
#order to calculate the variance at unit and cluster levels
 M0 <- glmer(birth_cert_recoded ~ 1 - (1 | district),
  data = HH_children_left_merged_df,
  family = binomial(link = "logit"),
  glmerControl(calc.derivs = FALSE) # We use this so that the model converges
)
summary(M0)
tab_model(M0, file = "M0_birth_cert.doc")

M0_level2 <- glmer (birth_cert_recoded ~ sex + wealth_idx + mother_edu_lvl + HH_head_religion_muslim 
   + HH_head_religion_sikh + HH_head_religion_others
  + HH_head_caste + (1|district),
  data =  HH_children_left_merged_df, 
  family = binomial(link = "logit"),
  glmerControl(calc.derivs = FALSE)
)

summary(M0_level2)
tab_model(M0_level2, file = "M0_level2_birth_cert.doc")
```


```{r}
# Plotting estimates of level 2 residuals obtained from the empty model
u0 <- ranef(M0, condVar = TRUE)
u0se <- sqrt(attr(u0[[1]], "postVar")[1, , ])
district_id <- rownames(u0[[1]])
u0tab <- cbind("district_id" = district_id,
               "u0" = u0[[1]],
               "u0se" = u0se)
colnames(u0tab)[2] <- "u0"
u0tab <- u0tab[order(u0tab$u0), ]
u0tab <- cbind(u0tab, c(1:dim(u0tab)[1]))
u0tab <- u0tab[order(u0tab$district_id), ]
colnames(u0tab)[4] <- "u0rank"
plot(
  u0tab$u0rank,
  u0tab$u0,
  type = "n",
  xlab = "District ID (j)",
  ylab = "Random District Level Intercept (u0j)",
  ylim = c(-4, 4)
)
segments(u0tab$u0rank,
         u0tab$u0 - 1.96 * u0tab$u0se,
         u0tab$u0rank,
         u0tab$u0 +
           1.96 * u0tab$u0se) + abline(h = 0, col = "red")
points(u0tab$u0rank, u0tab$u0, col = "blue")
```

**Intraclass correlation coefficient**

```{r}
# Calculating the intraclass correlation coefficient for birth certificate possession
icc_birth_cert <- M0@theta[1]^2/ (M0@theta[1]^2 + (pi^2/3))
icc_birth_cert
# icc is 0.03 --> 3% variance at districts
```

#### Aadhaar possession

```{r}
M_1_0 <- glmer(
  has_aadhaar_recoded ~ 1 - (1 | district),
  data = HH_othermems_left_merged_df,
  family = binomial(link = "logit"),
  glmerControl(calc.derivs = FALSE) # We use this so that the model converges
)
summary(M_1_0)
tab_model(M_1_0, file = "M0_aadhaar.doc")

M_1_0_level2 <- glmer (has_aadhaar_recoded ~ sex + wealth_idx + edu_lvl
   + HH_head_religion_muslim_othermems 
 + HH_head_religion_sikh_othermems   + HH_head_religion_others_othermems
  + HH_head_caste + (1|district),
  data =  HH_othermems_left_merged_df, 
  family = binomial(link = "logit"),
  glmerControl(calc.derivs = FALSE)
)

summary(M_1_0_level2)
tab_model(M_1_0_level2, file = "M0_level2_birth_cert.doc")
```


```{r}
# Plotting estimates of level 2 residuals obtained from the null model
u0_1 <- ranef(M_1_0, condVar = TRUE)
u0se_1 <- sqrt(attr(u0_1[[1]], "postVar")[1, , ])
district_id1 <- rownames(u0_1[[1]])
u0_1tab <- cbind("district_id1" = district_id1,
                 "u0_1" = u0_1[[1]],
                 "u0se_1" = u0se_1)
colnames(u0_1tab)[2] <- "u0_1"
u0_1tab <- u0_1tab[order(u0_1tab$u0_1), ]
u0_1tab <- cbind(u0_1tab, c(1:dim(u0_1tab)[1]))
u0_1tab <- u0_1tab[order(u0_1tab$district_id1), ]
colnames(u0_1tab)[4] <- "u0rank_1"
plot(
  u0_1tab$u0rank_1,
  u0_1tab$u0_1,
  type = "n",
  xlab = "District ID (j)",
  ylab = "Random District Level Intercept (u0j)",
  ylim = c(-4, 4)
)
segments(
  u0_1tab$u0rank_1,
  u0_1tab$u0_1 - 1.96 * u0_1tab$u0se_1,
  u0_1tab$u0rank_1,
  u0_1tab$u0_1 +
    1.96 * u0_1tab$u0se_1
) + abline(h = 0, col = "red")
points(u0_1tab$u0rank_1, u0_1tab$u0_1, col = "blue")
```

**Intraclass correlation coefficient**

```{r}
# Calculating the intraclass correlation coefficient for Aadhaar possession
icc_aadhaar <- M_1_0@theta[1]^2/ (M_1_0@theta[1]^2 + (pi^2/3))
icc_aadhaar
#0.2159622 --> 21.7% at districts
```


### Fixed effects model

These models have individual level effects and fixed effects for districts

#### Birth certificate possession

```{r}
# Fixed effects model with only control variables
M2_fixedeff <- glm(
  birth_cert_recoded ~ sex + wealth_idx + mother_edu_lvl + HH_head_religion_muslim 
   + HH_head_religion_sikh + HH_head_religion_others
  + HH_head_caste + (district),
  data = HH_children_left_merged_df,
  family = binomial(link = "logit")
)
summary(M2_fixedeff)
tab_model(M2_fixedeff)
M2_birth_cert_margins <- margins(M2_fixedeff)
M2_birth_cert_margins_summary <- summary(M2_birth_cert_margins)
write.csv(M2_birth_cert_margins_summary, "M2_birth_cert_margins_summary.csv")

```

#### Aadhaar possession

```{r}
# Fixed effects model with only control variables
M2_1_fixedeff <- glm(
  has_aadhaar_recoded ~ sex + wealth_idx + edu_lvl
   + HH_head_religion_muslim_othermems
  + HH_head_religion_sikh_othermems  + HH_head_religion_others_othermems
  + HH_head_caste + (district),
  data = HH_othermems_left_merged_df,
  family = binomial(link = "logit")
)
summary(M2_1_fixedeff)
tab_model(M2_1_fixedeff)
M2_aadhaar_margins <- margins(M2_1_fixedeff)
M2_aadhaar_margins_summary <- summary(M2_aadhaar_margins)
write.csv(M2_aadhaar_margins_summary, "M2_aadhaar_margins_summary.csv")
```

### Random slopes models

Finally, I run random slopes models with all individual and district level 
variables, and include random slopes for each district level variables in a new 
equation.

#### Birth certificate possession

Model for **night lights**

```{r}
# Adding the all the level 2 independent variables to the control variable model
# equation and including the variable for night lights as the random slope
M3_night_lights <- glmer(
  birth_cert_recoded ~ sex + wealth_idx + mother_edu_lvl + HH_head_religion_muslim  
  + HH_head_religion_sikh + HH_head_religion_others + HH_head_caste 
  + viirs_annual_mean + tri_mean + vcf_mean + (1 + viirs_annual_mean | district),
  data = HH_children_left_merged_df,
  family = binomial(link = "logit"),
  glmerControl(calc.derivs = FALSE),
  nAGQ = 1
)
summary(M3_night_lights)
M3_night_lights_birth_cert_margins <- margins(M3_night_lights)
M3_night_lights_birth_cert_margins_summary <- summary(M3_night_lights_birth_cert_margins)
write.csv(M3_night_lights_birth_cert_margins_summary, "M3_night_lights_birth_cert_margins_summary.csv")
tab_model(M3_night_lights)
```

```{r}
# Model likelihood ratio test in comparison to the empty model
anova(M3_night_lights, M0, test = "Chi")
```

Now, we have ruggedness of terrain as the random slope.

```{r}
# Adding the all the level 2 independent variables to the control variable model 
# equation and including the variable for ruggedness as the random slope
M3_ruggedness <- glmer(
  birth_cert_recoded ~ sex + wealth_idx + mother_edu_lvl
   + HH_head_religion_muslim + HH_head_religion_sikh + HH_head_religion_others
  + HH_head_caste + viirs_annual_mean + 
    tri_mean + vcf_mean + (1 + tri_mean | district),
  data = HH_children_left_merged_df,
  family = binomial(link = "logit"),
  glmerControl(calc.derivs = FALSE),
  nAGQ = 1
)
summary(M3_ruggedness)
M3_ruggedness_birth_cert_margins <- margins(M3_ruggedness)
M3_ruggedness_birth_cert_margins_summary <- summary(M3_ruggedness_birth_cert_margins)
write.csv(M3_ruggedness_birth_cert_margins_summary, "M3_ruggedness_birth_cert_margins_summary.csv")
tab_model(M3_ruggedness)
```

```{r}
# Model likelihood ratio test in comparison to the the empty model
anova(M3_ruggedness, M0, test = "Chi")
```

And forest cover.

```{r}
# Adding the all the level 2 independent variables to the control variable model 
# equation and including the variable for forest cover as the random slope
M3_forest_cover <- glmer(
  birth_cert_recoded ~ sex + wealth_idx + mother_edu_lvl
 + HH_head_religion_muslim + HH_head_religion_sikh + HH_head_religion_others
 + HH_head_caste + viirs_annual_mean + 
    tri_mean + vcf_mean + (1 + vcf_mean | district),
  data = HH_children_left_merged_df,
  family = binomial(link = "logit"),
  glmerControl(calc.derivs = FALSE),
  nAGQ = 1
)
summary(M3_forest_cover)
M3_forest_cover_birth_cert_margins <- margins(M3_forest_cover)
M3_forest_cover_birth_cert_margins_summary <- summary(M3_forest_cover_birth_cert_margins)
write.csv(M3_forest_cover_birth_cert_margins_summary, "1M3_forest_cover_birth_cert_margins_summary.csv")
tab_model(M3_forest_cover)
```

```{r}
# Model likelihood ratio test in comparison to the empty model
anova(M3_forest_cover, M0, test = "Chi")
```

#### Aadhaar possession

Same comparisons as above, but now the outcome variable is is Aadhaar possession.

```{r}
# Adding the all the level 2 independent variables to the control variable model 
# equation and including the variable for night lights as the random slope
M3_1_night_lights <- glmer(
  has_aadhaar_recoded ~ sex + wealth_idx + edu_lvl
   + HH_head_religion_muslim_othermems 
 + HH_head_religion_sikh_othermems   + HH_head_religion_others_othermems
  + HH_head_caste + viirs_annual_mean + tri_mean 
  + vcf_mean + (1 + viirs_annual_mean | district),
  data = HH_othermems_left_merged_df,
  family = binomial(link = "logit"),
  glmerControl(calc.derivs = FALSE),
  nAGQ = 1
)
summary(M3_1_night_lights)
tab_model(M3_1_night_lights)
M3_night_lights_aadhaar_margins <- margins(M3_1_night_lights)
M3_night_lights_aadhaar_margins_summary <- summary(M3_night_lights_aadhaar_margins)
write.csv(M3_night_lights_aadhaar_margins_summary, "M3_night_lights_aadhaar_margins_summary.csv")
```

```{r}
# Model likelihood ratio test in comparison to the empty model
anova(M3_1_night_lights, M_1_0, test = "Chi")

```

```{r}
# Adding the all the level 2 independent variables to the control variable model 
# equation and including the variable for ruggedness as the random slope
M3_1_ruggedness <- glmer(
  has_aadhaar_recoded ~ sex + wealth_idx + edu_lvl
  + HH_head_religion_muslim_othermems  + HH_head_religion_sikh_othermems 
  + HH_head_religion_others_othermems
  + HH_head_caste + viirs_annual_mean + tri_mean + vcf_mean 
  + (1 + tri_mean | district),
  data = HH_othermems_left_merged_df,
  family = binomial(link = "logit"),
  glmerControl(calc.derivs = FALSE),
  nAGQ = 1
)
summary(M3_1_ruggedness)
tab_model(M3_1_ruggedness)
M3_ruggedness_aadhaar_margins <- margins(M3_1_ruggedness)
M3_ruggedness_aadhaar_margins_summary <- summary(M3_ruggedness_aadhaar_margins)
write.csv(M3_ruggedness_aadhaar_margins_summary, "M3_ruggedness_aadhaar_margins_summary.csv")
```

```{r}
# Model likelihood ratio test in comparison to the empty model
anova(M3_1_ruggedness, M_1_0, test = "Chi")
```

```{r}
# Adding the all the level 2 independent variables to the control variable model 
# equation and including the variable for forest cover as the random slope
M3_1_forest_cover <- glmer(
  has_aadhaar_recoded ~ sex + wealth_idx + edu_lvl
  + HH_head_religion_muslim_othermems  + HH_head_religion_sikh_othermems 
  + HH_head_religion_others_othermems
  + HH_head_caste + viirs_annual_mean + tri_mean 
  + vcf_mean + (1 + vcf_mean | district),
  data = HH_othermems_left_merged_df,
  family = binomial(link = "logit"),
  glmerControl(calc.derivs = FALSE),
  nAGQ = 1
)
summary(M3_1_forest_cover)
tab_model(M3_1_forest_cover)
M3_forest_cover_aadhaar_margins <- margins(M3_1_forest_cover)
M3_forest_cover_aadhaar_margins_summary <- summary(M3_forest_cover_aadhaar_margins)
write.csv(M3_forest_cover_aadhaar_margins_summary, "1M3_forest_cover_aadhaar_margins_summary.csv")
```

```{r}
# Model likelihood ratio test in comparison to the empty model
anova(M3_1_forest_cover, M_1_0, test = "Chi")
```

All done!
